---
title: "Assignment 2"
author: "igal tsirulnik, Yoni Elhanati"
date: "April 11, 2016"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(ggmap)
library(RCurl)
library(jsonlite)


```

## Description of the dataset-
Sales in Bloomfield Township, Michigan
fields:
X| Y|	RECORDDT|	SALEAMNT|	CNTASSDVAL|	SALESRATIO|	RESSTRTYPE|	RESYRBLT|	RESFLRAREA|	NGHBRHDCD|	LASTUPDATE


## Here you can see a small taste of the dataset-
```{r 1 name}
url <- 'https://services.arcgis.com/EZzgO87vB4k7XLB1/arcgis/rest/services/BloomfieldSales/FeatureServer/0/query?where=1%3D1&outFields=RECORDDT,SALEAMNT,RESYRBLT&outSR=4326&f=json'
web <- getURL(url)
raw <-fromJSON(web)
tmp <- lapply( raw, function(u) 
  lapply(u, function(x) if(is.null(x)) NA else x)
)
tmp <- lapply( tmp, as.data.frame )
head(tmp$features,5)

```

## Dataset on a map-
```{r 2 name}
# getting the map
map <- get_map(location = c(lon = mean(tmp$features$geometry.x), lat = mean(tmp$features$geometry.y)), zoom = 12,maptype = "terrain", scale = 2)
# plotting the map with some points on it
ggmap(map) +
  geom_point(data = tmp$features, aes(x = tmp$features$geometry.x, y = tmp$features$geometry.y , alpha = 0), size = 3, shape = 21) +  guides(fill=TRUE, alpha=FALSE, size=FALSE)

```

## Price destrebition by longtitude and altitude
```{r 3 name}
qplot(tmp$features$geometry.y, tmp$features$geometry.x, data=tmp$features,col= tmp$features$attributes.RECORDDT)
#it is clear  that as you get far from the center of the city prices of property goes down
```

## Analysis of the times buildngs were built in bloomfield
```{r 4 name}
barplot(table(tmp$features$attributes.RESYRBLT))
#we can see that the bigest part of the city was build around the 1950-1970 and since then development of the city slowed down

```

## Analysis of property prices compared to when they were built
```{r 5 name}
with(tmp$features,plot(tmp$features$attributes.RESYRBLT,tmp$features$attributes.SALEAMNT, xlim=c(1950,2008)))
#we can see that development has slowed down but the prices keep growing steadly

```


##Summury
the most relevant pieace of information, is location vs prices map, I would recomend to develop some script that can get input of price ranges and x,y (location) the output would be recomended places to look for property

